---
title: Using Mixed effect Cox model to study the factors associated with rate of SAVR in
  AS patients in Montreal
author: "Nancy Zhu"
date: "July 18, 2018"
output: 
  html_document:
    theme: flatly
    hightlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Introduction
A retrospective cohort study was designed to study the factors associated with the rate of SAVR (surgical aortic stenosis valve replacement) in aortic stenosis patients in Montreal. The study cohort was extracted from the RAMQ database:

**Inclusion criteria:**

Individuals aged >=67 who fulfilled one of the following 3 criterias between 2000-04-01 and 2011-03-31:

1. Had been diagnosed aortic stenosis during hospital admission

2. Had been diagnosed aortic stenosis at least twice during outpatient visits

3. Had been diagnosed aortic stenosis by a cardiologist during outpatient visits

The earliest date of diagnosis was used as the study entry date

**Exclusion criteria:**

1. Individuals with less than one year history in RAMQ database prior to study entry

**Study endpoints:**

1. Having SAVR (ascertained from physician billing information)

2. Death of all causes

3. Study end 2011-03-31


```{r,message=F,warning=F}
library(tableone)
library(survival)
library(coxme)
library(ggplot2)
library(dplyr)
library(lubridate)
cohort<-readRDS('data_for_cox.RData')
cohort$futime2<-as.numeric(cohort$futime)
cohort[,c('sociale_median','materielle_median')]<-lapply(cohort[,c('sociale_median','materielle_median')],as.factor)
```

#### Some descriptive analysis
Baseline characteristics:
```{r}
variables<-c('age_entry','futime2','sexe','diabete_combined','CKD','hypertension_combined',
             'pvd_combined','cad_combined','copd_combined','hyperlipidemia_combined','mi','sociale_median','materielle_median')
factor_vars<-c('sexe','diabete_combined','CKD','hypertension_combined',
               'pvd_combined','cad_combined','copd_combined','hyperlipidemia_combined','mi','sociale_median','materielle_median')

cohort[,factor_vars]<-lapply(cohort[,factor_vars],as.factor)

CreateTableOne(variables,'outcome',cohort,factorVars =factor_vars )
```


#### Mixed effect Cox model:
A mixed effect Cox model was used to investigate the association between socioeconomic status and the rate of SAVR in AS patients. A mixed model was choosen to address potential correlation introduced by geographic location. The random effect in the model is the FSA region for each individuals. The fixed effects are: Age at cohort entry, sex, material and social deprivation index, history of diabetes, hypertension, peripheral vascular disease, coronary heart disease, COPD, hyperlipidemia and acute myocardial infarction.

```{r}
# --- fit a mixed effect Cox model with FSA code as the cluster
m1 <- coxme(Surv(futime, outcome) ~ age_entry + sexe + materielle_median + 
              sociale_median + CKD+ mi + diabete_combined+ hypertension_combined + pvd_combined + cad_combined +
              copd_combined + hyperlipidemia_combined + (1 | pc), data = cohort)

summary(m1)

```

```{r}
# ----calculate confidence interval of coefficients:
#first get SE:
se<-sqrt(diag(vcov(m1)))
coeff<-m1$coefficients

# 95% CI is calculated as (exp(coeff-1.96*SE),exp(coeff+1.96*SE))
CI<-data.frame(low.95=exp(coeff-1.96*se),high.95=exp(coeff+1.96*se))
CI
```

Compare mixed effect model with a regular Cox model with no adjustment for geographic location:
```{r}
# --- fit a regular Cox model
m2<-coxph(Surv(futime, outcome) ~ age_entry + sexe + materielle_median + 
            sociale_median + CKD + mi + diabete_combined + hypertension_combined + pvd_combined + cad_combined + copd_combined + hyperlipidemia_combined, data = cohort)

summary(m2)

# --- compare two models:
anova(m1,m2)
```
From the anova test, it seems that there is no significant difference between the hierachical model and the normal Cox model, mainly because social and material deprivation index were measured based on FSA region, thus taking into account the regional variance.

#### Things to consider:
1. Test the hypothesis of the model

2. Fit Age as a categorical variable?
No, age is better kept as a continuous variable (less information loss)

3. Surprisingly, the follow up time between those who had surgery and those who didn't were close, suggesting death due to other causes needs to be taken in account.

#### Check proportional hazard assumption of the Cox model:
```{r}
test.ph <- cox.zph(m2)
test.ph
```
From the output above, the test is statistically significant for covariates CAD and Age, and the global test is also statistically significant. Therefore, the proportional hazards assumption is not met in this model.



```{r}
plot(test.ph[1], main='Schoenfeld residuals plot for Age')

#the hazard ratio increases at older age

plot(test.ph[16], main='Schoenfeld residuals plot for CAD')
```


#### Competing risk model:
```{r}
#recode outcome status: 0, censored 1, event 2,all cause mortality
cohort$outcome_competing<-cohort$outcome
cohort$outcome_competing[cohort$outcome==0&cohort$Dt_dec<ymd('2011-03-31')]<-2

```

```{r}
library(cmprsk)
cov<-model.matrix(~age_entry + sexe + materielle_median +      sociale_median + CKD + mi + diabete_combined + hypertension_combined +      pvd_combined + cad_combined + copd_combined + hyperlipidemia_combined,data=cohort)[,-1]

crr.model<-crr(cohort$futime,cohort$outcome_competing,cov)

summary(crr.model)
```

From the competing risk model, individuals who are socially deprived still showed a significant lower probability of having SAVR. 

**However, AS patients with history of myocardial infarction, peripheral vascular disease or coronary heart disease all showed significantly lower rate of getting SAVR independent of other variables. Can this be explained clinically? OR is that due to some residual confounding?**