---
title: "Mapping age standardized incidence AS rate in Greater Montreal Area"
author: "Nancy Zhu"
date: "June 19, 2018"
output: 
  html_document:
    theme: flatly
    hightlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,message=F,warning=F}
library(pacman)
p_load('dplyr','lubridate','ggplot2','rgdal','maptools','RColorBrewer','stringr','plotly','magrittr')


case_final_tb<-readRDS('case_age_incidence2.RData')
interv_final_tb<-readRDS('interv_age_incidence2.RData')
mi_final_tb<-readRDS('MI_age_incidence.RData')
sociale<-readRDS('sociale.RData')
materielle<-readRDS('materielle.RData')

#format the map:
fsa_map<-readOGR(dsn='FSA_map',layer='gfsa000b11a_e',encoding='UTF-8',stringsAsFactors = F)
fsa_data<-fsa_map@data

#subset map to Montreal region:
#need to get a list of FSA in Montreal (scrap from online)
fsacode<-read.csv('montreal_fsa.csv',stringsAsFactors = F,header=F)
fsacode<-unlist(str_extract_all(fsacode$V1,'H\\d{1}[[:upper:]]{1}'))
fsa_mtl<-fsa_map[fsa_data$CFSAUID %in% fsacode,]
fsa_data<-fsa_mtl@data
rm(fsa_map)


#merge age standardized rate to mapping:
fsa_mtl2<-fortify(fsa_mtl)
fsa_data$id<-row.names(fsa_data)
fsa_mtl2<-left_join(fsa_mtl2,fsa_data[,c(1,4)])
```


This plots shows age-standarized incidence rate of aortic stenosis (per 1000 population **above 60**) in Montreal between 2000 and 2010. Greater Montreal region was divided by 119 FSA regions. The number of incidence cases were ascertained from in-hospital diagnosis of aortic stenosis from RAMQ database.

Age-specific population data for each FSA area was extracted from Statistic Canada 2006 Census. And the 2006 Age-specific Canada population was used as the standard population.

```{r,warning=F, message=F}
age_incidence<-left_join(fsa_mtl2,case_final_tb,by=c('CFSAUID'='fsa_clean'))
age_incidence$age.standarized.rate[is.na(age_incidence$age.standarized.rate)]<-0

mapplot<-function(df,variable,title,color){

p<-ggplot(data=df,aes_string('long','lat',group='group',fill=variable,label='CFSAUID')) + 
  geom_polygon(color='gray70',size=0.2)+
  #coord_map(projection='albers',lat0=39,lat1=45)+
  theme(axis.line=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        axis.title=element_blank(),
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid=element_blank(),
        panel.spacing=unit(0, "lines"),
        plot.background=element_blank(),
        legend.justification = c(0.9,0.2),
        legend.position = c(0.6,0.2)
  )+
  ggtitle(title)

p<- p+scale_fill_distiller(type = "seq", palette = color, direction = 1)

ggplotly(p)
}

mapplot(age_incidence,'age.standarized.rate','Age-standarized incidence AS rate in Montreal \n from 2000-2011',14)

```


This plots shows the rate of surgical valve replacement(per 1000 population **above 60**) performed in Montreal between 2000 and 2010. Greater Montreal region was divided by 119 FSA regions.The number of SAVRs were ascertained from in-hospital interventions from RAMQ database.


```{r,message=F,warning=F}
interv_age_incidence<-left_join(fsa_mtl2,interv_final_tb,by=c('CFSAUID'='fsa_clean'))
interv_age_incidence$age.standarized.rate[is.na(interv_age_incidence$age.standarized.rate)]<-0

mapplot(interv_age_incidence,'age.standarized.rate','Age-standarized rate of AS surgical interventions in Montreal \n from 2000-2011',14)

```


##### Check for potential confounding:
The uneven distribution of AS incidence could be due to several confounders. In this graph, we are investigating the distribution of acute myocardial infarction in Montreal area. We suspect that since AS shares many common risk factors with myocardial infarction, individuals with MI are more likely to be diagnosed with AS due to more frequence hospital visit.

```{r,message=F,warning=F}
mi_age_incidence<-left_join(fsa_mtl2,mi_final_tb,by=c('CFSAUID'='fsa_clean'))
mi_age_incidence$age.standarized.rate[is.na(mi_age_incidence$age.standarized.rate)]<-0

mapplot(mi_age_incidence,'age.standarized.rate','Age-standarized rate of acute MI in Montreal \n from 2000-2011',1)

```


##### Exploring socio-economic status in Montreal

Introduction:

The Québec index of material and social deprivation is plotted in the following maps. The deprivation index consists of six socio-economic indicators, all derived from Canadian censuses, at the EA or DA levels. 

These indicators are:

1. the proportion of people aged 15 years and older with no high school diploma (SCOLAR)

2. the population/employment ratio of people aged 15 years and older (EMPLOI)

3. the average income of people aged 15 years and older (REVENU)

4. the proportion of individuals aged 15 years and older living alone (SEULES)

5. the proportion of individuals aged 15 years and older whose marital status is either
separated, divorced, or widowed (S_D_V)

6. the proportion of single-parent families (F_MONO).

Principal components analysis (PCA), a form of factor analysis, is the method used to combine socio-economic indicators in the form of a deprivation index. PCA carried out for Québec revealed **two components**, one said to be material, the other social.**The first reflects mainly education, employment and income**, and **the second, marital status (being widowed,separated, or divorced), living alone, or being in a single-parent family.** The Québec deprivation index is thus two-dimensional, with a material component and a
social component that can be examined separately or jointly. 


Source: https://www.inspq.qc.ca/pdf/publications/1258_QcIndexDeprivation1991-2006.pdf

The following 2 maps shows the median quintile of social and material components score in each FSA region in montreal between 2001 and 2011. A score of 1 means least-deprived, while a score of 5 means highly-deprived.

```{r,message=F,warning=F}
sociale<-left_join(fsa_mtl2,sociale,by=c('CFSAUID'='cp3'))
materielle<-left_join(fsa_mtl2,materielle,by=c('CFSAUID'='cp3'))

mapplot(materielle,'materielle_median','Material deprivation in Montreal between \n 2001 and 2011',3)
```

```{r,message=F,warning=F}
mapplot(sociale,'sociale_median','Social deprivation in Montreal between \n 2001 and 2011',3)
```

