---
title: "Poisson regression model-Updated with confounders"
author: "Nancy Zhu"
date: "August 28, 2018"
output: 
  html_document:
    theme: flatly
    hightlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file shows my first attempt to fit a poisson regression model to study the association between the rate of SAVR among AS patients and factors such as Age, SES status in different Montreal FSA regions between 2001 and 2010.

The data looks like this:
```{r,message=F,warning=F}
library(magrittr)
library(dplyr)
ds<-readRDS('dataset_poisson.RData')
ds%<>%rename(agegrp=V5)
ds2<-readRDS('dataset_poisson2.RData')
head(ds,10)
```

Now, run a simple poisson regression model:
```{r}
fit <- glm(interv ~ agegrp + materielle_median + sociale_median + offset(log(case)), data = ds, family = poisson)
result<-summary(fit)
result

exp(coef(result))
```

Confidence interval of odds ratios:
```{r}
exp(confint(fit))
```


From the exponetiated coefficients, it seems that as the age increases, the rate of having SAVR decreases. As people are more socially or materially more deprived, the rate of having SAVR decreases.

Now, check over-dispersion of the model:
```{r}
data.frame(deviance(fit), df=fit$df.residual)

#deviance goodness of fit
p.value<-pchisq(fit$deviance, df=fit$df.residual, lower.tail=FALSE)

```

The dispersion parameter is `r deviance(fit)/fit$df.residual`, close to 1, thus the data is not too dispersed for the model fitted.

Since the p value from the goodness of fit test is `r p.value`, above 0.05. The null hypothesis cannot be rejected, thus the model fits the data.

**Things to improve for the analysis:**

1.0 in material and sociale deprivation index were treated as missing data and were removed in this analysis, however those variable can be imputed from previous information

2.Other variables like incidence of MI, hypertension were not incorportaed in this analysis. Residual confoundings


####Updated model:

1. imputed value for material and sociale deprivation index,where missing value was replaced with median value within the same reference year and postal code region; if missing value happend for a postal code region, values were imputed based on the same reference year with a previous postal code region

2. acute MI, Chronic kidney disease, diabetes, dyslipidemia, peripheral vascular disease and hypertension were added as confounders.

Acute MI was ascertained from in-hospital admission diagnosis data, while the rest of the confounders were ascertained from a combination of in-hospital admission and prescription history. The first date of confounder ascertainment was defined as either the date of hospital discharge or first service date of prescription, whichever occured first. The data were grouped by postal code and a count of each confounder was obtained for each pc region over 10 years, the continous counts were transformed into 5 categories divided by quantiles.  

   
```{r}
fit2 <- fit <- glm(interv ~ V5 + materielle_median + sociale_median+ mi_cat+CKD+COPD+diabete+dyslipidemia+PVD+hypertension+offset(log(case)), data = ds2, family = poisson)

result2<-summary(fit2)
result2

exp(coef(result2))
```

Confidence interval of odds ratio:
```{r}
exp(confint(fit2))
```

